\bf Drift Removal for Time Series Data Using Quantile Trend Filtering

### 2019-01-03 Manuscript/extra_notes.tex
updated and organized manuscript

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
%% Assumptions environment
\newtheorem{assumption}[theorem]{Assumption}

\begin{document}
\title{Quantile Trend Filtering via Spingarn's Method}
\noindent
\textbf{Quantile Trend Filtering via Spingarn's Method}\\
\textbf{Date: \today}\\

%% ----------------------------------------------------------------------
%% Introduction
%% ----------------------------------------------------------------------
\section{Introduction}

@@

\textbf{Oh, Lee, and Nychka 2011 - Fast Nonparametric Quantile Regression With Arbitrary Smoothing Method} Unified framework for non-parametric quantile regression by approximating check loss function with quadratic loss near zero.\\
\textbf{Kim, Koh, Boyd, and Gorinevsky 2009} - Introduce the concept of l1 trend filtering.\\
\textbf{Tibshirani, 2014 - Adaptive piecewise polynomial estimation via trend filtering} Describes properties of trend filtering using quadratic loss. Shows that trend filtering estimates adapt to the local level of smoothness much better than smoothing splines, and exhibit
a remarkable similarity to locally adaptive regression splines. Prove that (with the right choice of tuning parameter) the trend filtering estimate
converges to the true underlying function at the minimax rate for functions whose kth derivative is of bounded variation.\\
\textbf{Ning, Selesnick, Duval 2014 - Chromatogram baseline estimation and denoising using sparsity (BEADS)} Address problem of estimating a smooth baseline in noisy data with drift. \\
We propose to use the trend filtering penalty with the check loss function to produce a non-parametric quantile regression estimate that can be computes using a linear time algorithm for removing trends in time series. Can be extended to model multiple quantiles and ensure non-crossing.

@@

We compare our detrending method with BEADS and the more general nonparametric quantile method introduced in  \cite{Oh2011}.

\bibliographystyle{abbrv}
\bibliography{detrendify}

\end{document}

>>>>

%\startlocaldefs
%\numberwithin{equation}{section}
%\theoremstyle{plain}
%\newtheorem{thm}{Theorem}[section]
%\endlocaldefs

\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

\pdfminorversion=4

\begin{document}
\def\spacingset#1{\renewcommand{\baselinestretch}%
	{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
	\title{\bf Drift Removal for Time Series Data Using Quantile Trend Filtering}
	\author{Halley Brantley\thanks{
			Department of Statistics, North Carolina State University, Raleigh, NC 27695 (E-mail: hlbrantl@ncsu.edu)} \,
		Joseph Guinness\thanks{
			Department of Statistics, North Carolina State University, Raleigh, NC 27695-8203 (E-mail: jsguinne@ncsu.edu)} \,
		and
		%    and
		Eric C. Chi\thanks{Department of Statistics, North Carolina State University, Raleigh, NC 27695-8203 (E-mail: eric$\_$chi@ncsu.edu).}    \\}
	\date{}
	\maketitle
} \fi

\if1\blind
{
	\bigskip
	\bigskip
	\bigskip
	\begin{center}
		{\LARGE\bf Title}
	\end{center}
	\medskip
} \fi

\bigskip
\begin{abstract}
	Abstract
\end{abstract}

\noindent%
{\it Keywords:}  Key words
\vfill

\newpage
\spacingset{1.45} % DON'T change the spacing!
%% ----------------------------------------------------------------------
%% Introduction
%% ----------------------------------------------------------------------
\section{Introduction}

@@

\begin{itemize}
	\item \cite{Oh2011} unified framework for non-parametric quantile regression by approximating check loss function with quadratic loss near zero.
	\item \cite{KoenkerNgPortnoy1994} introduce quantile smoothing splines. We need to discuss how our approach is different.
	\item \cite{Kim2009} introduce the concept of $\ell_1$-trend filtering.
	\item \cite{Tib2014} describes properties of trend filtering using quadratic loss. Shows that trend filtering estimates adapt to the local level of smoothness much better than smoothing splines, and exhibit a remarkable similarity to locally adaptive regression splines. Prove that (with the right choice of tuning parameter) the trend filtering estimate
	converges to the true underlying function at the minimax rate for functions whose kth derivative is of bounded variation.
	\item \cite{Ning2014} address problem of estimating a smooth baseline in noisy data with drift.
	\item \cite{Takeuchi2006nonparametric} Nonparametric quantile regression using SVM with Gaussian RBF kernels and check (pinball) loss. 
	\item \cite{yuan2006gacv} Comparison of cross-validation methods for quantile smoothing splines.  
\end{itemize}
We propose to use the trend filtering penalty with the check loss function to produce a non-parametric quantile regression estimate that can be computes using a linear time algorithm for removing trends in time series. The formulation was proposed by \cite{Kim2009} as a possible extension of $\ell_1$-trend filtering but not studied. Moreover we extend the basic framework to model multiple quantiles and ensure non-crossing.

@@

We compare our detrending method with BEADS and the more general nonparametric quantile method introduced by \cite{Oh2011}.

\section{ADMM for Smoothing Windows}

To our knowledge, no one has addressed the problem of finding smooth quantile trends of series that are too large to be processed simultaneously. We propose an alternating direction method of multipliers (ADMM) algorithm for solving large problems in a piecewise fashion. The ADMM algorithm, described by \cite{boyd2011distributed}, relies on the idea of dual ascent. If we consider the equality optimization problem 
\begin{align}
&\text{minimize } f(x)\\
&\text{subject to } Ax = b
\end{align}
with variable $x\in \mathbf{R}^n$, where $A \in \mathbf{R}^{mxn}$ and $f: \mathbf{R}^n \rightarrow \mathbf{R}$ is convex. The corresponding Lagrangian function is 
\begin{equation}
L(x,\omega) = f(x) + \omega^T(Ax-b)
\end{equation}
and the corresponding dual problem  is 
\begin{equation}
\text{maximize } \inf_x L(x,\omega)
\end{equation}
Assuming that strong duality holds (Slater's constraint: there exists a solution in the interior of the domain), the optimal values of the primal and dual variables are the same. The dual ascent method, uses gradient ascent to solve the dual problem and thus the primal problem using the iterates
\begin{align}
&x^{k+1} = \arg\min L(x, \omega^k)\\
&\omega^{k+1} = \omega^k + \alpha^k(Ax^{k+1} - b)
\end{align}
where $\alpha^k > 0$ is a step size and $k$ is the iteration counter. In many cases (including our problem), the $x$ update fails because the problem is unbounded below. To remedy this issue the augmented Lagrangian was introduced:
\begin{equation}
L_{\gamma}(x,\omega) = f(x)+\omega^T(Ax-b) + \frac{\gamma}{2}||Ax-b||_2^2
\end{equation}
where $\gamma > 0$ is called the penalty parameter. Applying dual ascent to the modified problem results in the method of multipliers algorithm which converges under more general conditions:
\begin{align}
&x^{k+1} = \arg\min L_\gamma(x, \omega^k)\\
&\omega^{k+1} = \omega^k + \gamma(Ax^{k+1} - b)
\end{align}
Consider a new optimization problem with a separable objective function. 
\begin{align}
&\text{minimize } f_1(x_1) + f_2(x_2)\\
&\text{subject to } A_1x_1 + A_2x_2 = b
\end{align}
where $x = (x_1, x_2)$, $i \in \{1,2\}$, and  $x_i \in \mathbf{R}^{n_i}$. The dual ascent updates can be expressed as 
\begin{align}
&x_i^{k+1} = \arg\min L_i(x_i, \omega^k)\\
&\omega^{k+1} = \omega^k + \alpha^k(Ax^{k+1} - b)
\end{align}
however we lose the separability if the augmented Lagrangian is used instead, i.e. the augmented Lagrangian can not be separated into functions of $x_i$.  The Alternating Direction Method of Multipliers (ADMM) addresses this problem and maintains separability while using the augmented Lagrangian to improve convergence through the following updates
\begin{align}
&x_1^{k+1} = \arg\min_{x_1} L_{\gamma}(x_1, x_2^k, \omega^k)\\
&x_2^{k+1} = \arg\min_{x_2} L_{\gamma}(x_1^{k+1}, x_2, \omega^k)\\
&\omega^{k+1} = \omega^k + \alpha^k(A_1x_1^{k+1} + A_2x_2^{k+1} - b)
\end{align}

We now consider the quantile regression trend filtering problem,  
\begin{equation}
\text{minimize } \rho_\tau(y-\theta) + \lambda||D^{(k)}\theta||_1\\
\end{equation}
where $y,\theta \in \mathbf{R}^n$, $y$ is the observed data, $\rho_{\tau}(u) = \sum_i(\tau - I(u_i < 0))u_i$ is the check loss function corresponding to quantile level $\tau$ and $D^{(k)}$ is the discrete differencing matrix of order $k$ and $\lambda$ is a tuning parameter that controls smoothness. We first re-parameterize $\phi = y-\theta$ so the problem is
\begin{equation}
\text{minimize } \rho_\tau(\phi) + \lambda||D^{(k)}(y-\phi)||_1\\
\end{equation}
We further divide $\phi$ order to solve smaller problems: Defining
\begin{align}
&\phi_1 = (\phi_{11}, \phi_{12})\\
&\phi_2 = (\phi_{21}, \phi_{22}, \phi_{23})\\
&\phi_3 = (\phi_{31}, \phi_{32})\\
&\phi = (\phi_{11}, \phi_{12}=\phi_{21}, \phi_{22}, \phi_{23}=\phi_{31}, \phi_{32}) \\
\end{align}
Dividing $y$ similarly, the problem then becomes 
\begin{align}
&\text{minimize } \sum_{i=1}^3 \rho_\tau(\phi_i) + \lambda||D^{(k)}(y_i-\phi_i)||_1\\
&\text{subject to: } \phi_{12}=\phi_{21}, ~~ \phi_{23}=\phi_{31}\\
\end{align}
We can further simplify by defining 
\begin{align}
&\overline{\phi} = (\phi_{11}, \frac{\phi_{12}+\phi_{21}}{2}, \phi_{22}, \frac{\phi_{23}+\phi_{31}}{2}, \phi_{32}) \\
&\overline{\phi_1} = (\phi_{11}, \frac{\phi_{12}+\phi_{21}}{2})\\
&\overline{\phi_2} = ( \frac{\phi_{12}+\phi_{21}}{2}, \phi_{22}, \frac{\phi_{23}+\phi_{31}}{2})\\
&\overline{\phi_3} = (\frac{\phi_{23}+\phi_{31}}{2}, \phi_{32})
\end{align}
so the problem becomes
\begin{align}
&\text{minimize } \sum_{i=1}^3 \rho_\tau(\phi_i) + \lambda||D^{(k)}(y_i-\phi_i)||_1\\
&\text{subject to: } \phi_{i}=\overline{\phi_i}\\
\end{align}
The augmented Lagrangian for this problem is 
\begin{align}
&L_\gamma(\phi_1,\phi_2, \phi_3, \overline{\phi_1}, \overline{\phi_2}, \overline{\phi_3}, \omega) = \\
&\sum_{i=1}^3 \rho_\tau(\phi_i) + \lambda||D^{(k)}(y_i-\phi_i)||_1 + \omega_i^T(\phi_i - \overline{\phi_i}) + \frac{\gamma}{2}||\phi_i - \overline{\phi_i}||_2^2
\end{align}
The ADMM updates are then given by
\begin{align}
&\phi_i^{k+1} = \arg\min_{\phi_i}\rho_\tau(\phi_i) + \lambda||D^{(k)}(y_i-\phi_i)||_1 + \omega_i^{kT}(\phi_i - \overline{\phi_i}^k) + \frac{\gamma}{2}||\phi_i - \overline{\phi_i}^k||_2^2\\
&\omega_i^{k+1} = \omega_i^{k} + \gamma(\phi_i^{k+1} - \overline{\phi_i}^{k+1})
\end{align}
The $\phi_i$ updates can be obtained using a quadratic program solver such as Gurobi and can be obtained in parallel.

\pagebreak

\begin{figure}[!h] 
	\caption{Windows fit separately compared to simultaneous fit, no signal present.}
	\includegraphics[width = \linewidth]{Figures/overlapping_windows.png}
\end{figure}

\begin{figure}[!h] 
	\caption{Windows fit with 150 iterations of ADMM, no signal present.}
	\includegraphics[width = \linewidth]{Figures/admm_windows.png}
\end{figure}

\begin{figure}[!h] 
	\caption{Windows fit separately compared to simultaneous fit, signal present.}
	\includegraphics[width = \linewidth]{Figures/overlapping_windows2.png}
\end{figure}

\begin{figure}[!h] 
	\caption{Windows fit with 300 iterations of ADMM, signal present.}
	\includegraphics[width = \linewidth]{Figures/admm_windows2.png}
\end{figure}

\pagebreak

\section {Cross Validation Methods}
Our method can easily handle missing data by changing the check loss function to output 0 for missing values. This allows us to leave out validation observations that can be used to select the tuning parameter $\lambda$ and to compare method performance on real data. A number of methods have been proposed for selecting the quantile regression smoothing spline tuning parameter \cite{yuan2006gacv}. The traditional smoothing spline for $y \in \mathbf{R}^n$ as a function of a predictor $x \in \mathbf{R}^n$ using the squared loss is estimated by minimizing

\begin{equation}
\frac{1}{n}\sum_i (y_i - f(x_i))^2 + \lambda \int(f''(x))^2 dx
\end{equation}

It has been shown that the solution to this problem is a cubic spline with a knot at each of the observed $x_i$. This problem can then be reformulated using a spline basis matrix $B \in \mathbf{R}^{nxn}$: 
\begin{equation}
(y-B\beta)^T(y-B\beta) + n\lambda\beta^T\Omega\beta
\end{equation}  
where $\Omega_{jk} = \int B_j''(x)B_k''(x)dx$. Since each spline basis function is a defined as a cubic polynomial with non-zero second derivatives on a finite region, the integrals are finite. The solution is then given by 
$$f(x) = B\widehat{\beta} = B(B^TB + n\lambda\Omega)^{-1}B^Ty$$
Because the solution is a linear combination of the observed $y$, the leave-one-out cross validation (LOOCV) statistics can be calculated without refitting the model. Defining $W = B\widehat{\beta} = B(B^TB + n\lambda\Omega)^{-1}B$ the LOOCV residual is given by 
\begin{equation}
y_i - \widehat{y_i}^{(-i)} = \frac{y_i - \widehat{y_i}}{1-W_{[i,i]}}
\end{equation}
where $\widehat{y_i}$ is the prediction using the full dataset and $\widehat{y_i}^{(-i)}$ is the prediction from the model fit without $y_i$. In practice, generalized cross validation (GCV) has also been found to be an effective metric for choosing the smoothing parameter, with the validation MSE calculated as 
\begin{equation}
\frac{\frac{1}{n}\sum(y_i-\widehat{y_i})^2}{(1-\frac{1}{n}tr(W))^2}
\end{equation}

Returning to the quantile regression case, \cite{nychka1995nonparametric} proposed a pseudo-data algorithm for a quantile spline estimator of the form 
\begin{equation}
\sum_i \rho_{\tau}(y_i - g(x_i)) + \lambda\int(g''(x))^2dx.
\end{equation}

If $\rho_{\tau}(\cdot)$ were differentiable, the solution to this equation would take a form similar to that of the squared loss smoothing spline with weights equal to $\frac{\rho'_{\tau}(y_i-g(x_i))}{2(y_i - g(x_i))}$. Relying on this idea, Nychka proposed to solve the problem by iteratively solving the weighted smoothing spline. To address the non-differentiability they propose an approximation 
\begin{equation}
\rho_{\tau, \delta}(u) = [\tau I(u>0) + (1-\alpha)I(u<0)]u^2/\delta
\end{equation}
They propose a corresponding approximate cross validation metric for choosing the tuning parameter:
\begin{equation}
ACV(\lambda) = \frac{1}{n}\sum_i \rho_{\tau}\left(\frac{y_i - \widehat{g}_\lambda(x_i)}{1-h_{ii}}\right)
\end{equation}
where $h_{ii} = \frac{\partial\widehat{g}_{\tau, \lambda}(x_i)}{\partial y_i}$. However \cite{yuan2006gacv} showed through simulation that this is not a good approximation to the robust cross validation score
\begin{equation}
RCV(\lambda) = \frac{1}{n}\sum\rho_{\tau}(y_i - g_\lambda^{(-i)}(x_i))
\end{equation}
and propose the GACV as an alternative 
\begin{equation}
GACV(\lambda) = \sum_i \rho_{\tau}\left(\frac{y_i - \widehat{g}_\lambda(x_i)}{n-tr(H)}\right)
\end{equation}
where $H_{ij} = \frac{\partial\widehat{g}_{\tau, \lambda}(x_i)}{\partial y_j}$

\cite{KoenkerNgPortnoy1994} proposed a quantile smoothing spline using the check loss function and 1-norm rather than 2-norm:
\begin{equation}
R_{\tau,\lambda} = \rho_{\tau}(y - g(x)) + \lambda\int_0^1|g''(x)|dx
\end{equation}
with $0 = x_0 < ... < x_n = 1$. They prove that the resulting function $\widehat{g(x)}$ is a linear spline with knots at the observed values of $x$. They also argue that the solutions $\widehat{g}_{\tau,\lambda}(\cdot)$ are piecewise constant in $\lambda$ and that there exists a mesh $0= \lambda_0 < \lambda_1 < ... < \lambda_J$ such that $\widehat{g}_{\tau,\lambda}(\cdot)$ is the solution for all $\lambda \in [\lambda_{i-1}, \lambda_i]$. Relating $\lambda$ to the number of interpolated points $p_{\lambda} = \sum I(y_i = \widehat{g}_i(x_i))$, which can be thought of as active knots, they propose the Schwarz criterion for the selection of $\lambda$
\begin{equation}
SIC(p_{\lambda}) = log[n^{-1}\sum\rho_{\tau}(y_i - \widehat{g}(x_i))] + \frac{1}{2n}p_{\lambda}log n
\end{equation}

\section{Simulation Study}

\subsection*{Methods}
We compare the performance of our quantile trend filtering method with the three previously published methods using designs proposed by \cite{Racine2017}. The methods compared are

\begin{itemize}
	\item \texttt{npqw}: \cite{Racine2017} constrain the response to follow a smooth location scale model of the form $Y_i = a(X_i) + b(X_i)\epsilon_i$. They estimate the $\tau$\textsubscript{th} conditional quantile given $X_i = x$ using a kernel estimator
	\begin{equation}
		q_{\tau}(x) = \frac{\sum_{i=1}^n \Phi^{-1}_{(Y_i, b(X_i))}(\delta_0)K_h(X_i,x)}{\sum_{i=1}^nK_h(X_i, x)}
	\end{equation}
	defining $\Phi^{-1}_{(Y_i, b(X_i))}(\delta_0)$ as the quantile function of the Normal distribution with mean $Y_i$ and standard deviation $b(X_i)$ evaluated at $\tau$. $\delta_0$ is a function of $\tau$ and chosen empirically, $h$ is a tuning parameter and $K$ is a kernel function. Code was obtained from the author for the \texttt{quantile-ll} method.

	\item \texttt{qsreg}: \cite{Oh2011} proposed a pseudo-data algorithm for a quantile spline estimator of the form 
	\begin{equation}
	\sum_i \rho_{\tau}(y_i - g(x_i)) + \lambda\int(g''(x))^2dx.
	\end{equation} 
	If $\rho_{\tau}(\cdot)$ were differentiable, the solution to this equation would take a form similar to that of the squared loss smoothing spline with weights equal to $\frac{\rho'_{\tau}(y_i-g(x_i))}{2(y_i - g(x_i))}$. Relying on this idea, Nychka proposed to solve the problem by iteratively solving the weighted smoothing spline. To address the non-differentiability they propose an approximation 
	\begin{equation}
	\rho_{\tau, \delta}(u) = [\tau I(u>0) + (1-\alpha)I(u<0)]u^2/\delta
	\end{equation}
	The function \texttt{qsreg} in the \texttt{fields} R package was used. The smoothing parameter is chosen automatically using generalized cross validation on the pseudo data.

	\item \texttt{rqss}: \cite{KoenkerNgPortnoy1994} Koenker proposed smoothing splines using trend filtering with the second order differencing matrix which results in linear splines. The function \texttt{rqss} in the \texttt{quantreg} package implements this method. The smoothing parameter $\lambda$ is chosen using a grid search and minimizing 
	\begin{equation}
	SIC(p_{\lambda}) = log[n^{-1}\sum\rho_{\tau}(y_i - \widehat{g}(x_i))] + \frac{1}{2n}p_{\lambda}log n
	\end{equation}
	where $p_{\lambda} = \sum I(y_i = \widehat{g}_i(x_i))$, which can be thought of as active knots.

	\item \texttt{detrendr\_SIC}: Our method where we minimize
	$\sum_i\rho_{\tau}(y_i - \theta_i) + \lambda||D\theta||_1$ and $\lambda$ is chosen using SIC from above. A single value of $\lambda$ was chosen by scaling and summing SIC values across all quantiles. 
	\item \texttt{detrendr\_valid}: Our method where lambda is chosen by leaving out every 5th observation as a validation data set and evaluating the check loss function on the validation data.
	\item \texttt{detrendr\_eBIC}:   The traditional BIC is given by 
	\begin{equation}
	\mbox{BIC}(s) = -2\log(L\{\hat{\theta}(s)\}) + \nu(s)\log n 
	\end{equation}	
	where $\theta(s)$ is the parameter $\theta$ with those components outside $s$ being set to 0, and $\nu(s)$ is the number of components in $s$. If we assume an asymmetric Laplace likelihood $L(y|\theta) = \left(\frac{\tau^n(1-\tau)}{\sigma}\right)^n\exp\left\{-\sum_i\rho_\tau(\frac{y_i - \theta_i}{\sigma})\right\}$ and the number of non-zero elements of $D\theta$ as $df$
	\begin{equation}
	\mbox{BIC}(df) = 2\sum_i\frac{1}{\sigma}\rho_{\tau}(y_i-\theta_i) + df\log n
	\end{equation} 
	We can choose and $\sigma>0$ and have found empirically that $\sigma =  \frac{1-|1-2\tau|}{2}$ produces stable estimates. \cite{chen2008} proposed the extended BIC for large parameter spaces 
	\begin{equation}
	BIC_{\gamma}(s) = -2\log(L\{\hat{\theta}(s)\}) + \nu(s)\log n  + 2\gamma\log{P\choose j,}~~\gamma \in [0,1]
	\end{equation}
	where $P$ is the total number of possible parameters and $j$ is the number of parameters included in given model. We used this criteria with $\gamma = 1$, $P=n-k$ where $k$ is the order of the differencing matrix and $j = \nu(s)$ is the number of non-zero entries in $D^{(k)}\theta$.

\end{itemize}

\subsection*{BIC examples}

We used a single dataset to illustrate the difference between the scaled, unscaled and extended BIC criteria.

\begin{figure}[h!]
	\caption{Degrees of freedom (number of non-zero elements of $D\theta$) by $\log(\lambda)$.} 
	\includegraphics[width = 0.25\linewidth]{Figures/BIC_data.png}
	\includegraphics[width = 0.25\linewidth]{Figures/df_by_lambda.png}
	\includegraphics[width = 0.5\linewidth]{Figures/BIC_by_lambda.png}
\end{figure}

\subsection*{Design}
Three simulation designs from \cite{Racine2017} were considered. For all designs $X_i$ was generated as a uniformly spaced sequence in $[0,1]$ and the response $Y$ was generated as 
$$Y_i = sin(2\pi x_i) + \epsilon_i(x_i)$$
The three error distributions considered were 
\begin{itemize}
 \item Gaussian: $\epsilon_i(x_i) \sim N\left(0, \left(\frac{1+x_i^2}{4}\right)^2\right)$
 \item Beta: $\epsilon_i \sim Beta(1, 11-10x_i)$
\item Mixed normal: $\epsilon_i$ is simulated from a mixture of $N(-1,1)$ and  $N(1,1)$ with mixing probability $x_i$.
\end{itemize}
\begin{figure}
\caption{Simulated data with true quantiles $\tau \in \{0.01, 0.05, 0.25, 0.5, .75, 0.95, 0.99\}$}	
\includegraphics[width=.3\linewidth]{Figures/gaus.png}
\includegraphics[width=.3\linewidth]{Figures/shapebeta.png}
\includegraphics[width=.3\linewidth]{Figures/mixednorm.png}
\end{figure}

100 datasets were generated of sizes 300, 500 and 1000. The MSE was calculated as $\frac{1}{n}\sum_i (\hat{q}_{\tau}(x_i) - q_\tau(x_i))^2$. The plots below show the mean MSE $\pm$ twice the standard error by method, quantile level and sample size.

\includegraphics[width=\linewidth]{Figures/gaus_mse.png}

\includegraphics[width=\linewidth]{Figures/shapebeta_mse.png}

\includegraphics[width=\linewidth]{Figures/mixednorm_mse.png}

\section{Peaks Simulation}
We use another simulation design based on the applied problem we aim to solve. We assume that the measured data can be represented by 
\begin{equation}
Y(t) = s(t) + b(t) + \epsilon
\end{equation} 
where $s(t)$ is the true signal at time $t$, $b(t)$ is the drift component that varies smoothly over time and $\epsilon \sim N(0, \sigma^2)$ is an error component. We assume $t$ is a uniformly spaced sequence between 0 and 1. We generate $b(t)$ using a cubic natural spline basis function with degrees of freedom sampled from $n/50$ to $n/25$ with equal probability, and coefficients drawn from an exponential distribution with rate 1. The true signal function is assumed to be zero with Gaussian peaks. The number of peaks is sampled from $n/100$ to $n/50$ with equal probability with centers uniformly distributed between 0.1 and 0.9 and bandwidths uniformly distributed between $1/n$ and $5/n$ and areas uniformly distributed between 0 and $20/n$. One hundred datasets were generated for $n=\{300,500,1000, 5000\}$. We compare the methods ability to estimate the true quantiles of $b(t) + \epsilon$  for $\tau \in \{0.01, 0.05, 0.1\}$ and calculate the RMSE.

\begin{figure}
	\caption{Example of simulated peaks, baseline, and observed measurements.}
	\includegraphics[width = \linewidth]{Figures/ex_peaks.png}
\end{figure}

\begin{figure}[h!]
	\caption{RMSEs compared to the simulated baseline function.}
	\includegraphics[width = \linewidth]{Figures/peaks_mse.png}
\end{figure}

\begin{figure}[h!]
	\caption{Example signal classification using threshold. Red indicates true signal > 0.1, blue indicates classified as signal after baseline removal using eBIC detrendr and a threshold of 1.}
	\includegraphics[width = \linewidth]{Figures/peaks_eg_class.png}
\end{figure}

\begin{figure}[h!]
	\caption{Miss-classification rates by threshold and method, values above the upper limit (npqw) not shown.}
	\includegraphics[width = \linewidth]{Figures/peaks_missclass.png}
\end{figure}

\section{Application}

\begin{figure}
	\caption{Example of simulated peaks, baseline, and observed measurements.}
	\includegraphics[width = \linewidth]{Figures/uncorrected_data.png}
	\includegraphics[width = \linewidth]{Figures/corrected_data.png}
	\includegraphics[width = \linewidth]{Figures/corrected_zoom_data.png}
\end{figure}

\pagebreak

\bibliographystyle{asa}
\bibliography{detrendify}
\end{document}
